\documentclass[tikz, 12pt]{article}

\usepackage[margin=1.5in]{geometry}
\usepackage[table]{xcolor}
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{amssymb}
\captionsetup{justification=raggedright,singlelinecheck=false,format=hang}
\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc} 
\usepackage{blindtext}
\usepackage{authblk}
\usepackage{listings}
\usepackage{blindtext}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{lipsum}
\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
\renewcommand{\labelenumii}{\theenumii}
\renewcommand{\theenumii}{\theenumi.\arabic{enumii}.}
\usetikzlibrary{positioning,fit,calc,arrows}
\tikzset{block/.style={draw,thick,text width=2cm,minimum height=1cm,align=center},
         line/.style={-latex}
}
\theoremstyle{definition}
\newtheorem{defn}{Definition}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\title {Game Channels: state channels for the gambling industry with built-in PRNG}
\author[1]{Alisa Cherniaeva}
\author[1]{Ilia Shirobokov} 
\author[2]{Alexander Davydov}
\affil[1]{BlockProof Tech LLC\thanks{research@blockproof.tech}}
\affil[2]{DAO.Casino\thanks{research@dao.group}}
\date {November 2018\footnote{Revised  September 2019}}
\hyphenation{every-where}
\begin{document}
\maketitle
	\begin{abstract}
Blockchain technology has immense potential. At the same time, it is not always possible to scale blockchains. State Channels solve the problem of scalability while increasing the blockchain's speed and efficiency. State Channels present a workaround to current blockchains' TPS (transaction per second) bottleneck. We used State Channels as a foundation and created Game Channels. We built it around the needs of the gambling market. We also developed Signidice PRNG as well as a dispute resolution mechanism. Signidice uses unique digital signatures and is also described below. The potential use of Game Channels technology is not only gambling; some types of online gaming may also be able to use it.

	\end{abstract}
\tableofcontents	
	\input{sections/Introduction}
	\input{sections/preliminaries}
		\input{sections/description}
\input{sections/modifications}
\section*{Acknowledgements}
We would like to thank research scientist Mark Reynolds for proofreading and feedback.

We also thank Maria Kondorskaya for her help with translation.  

And we thank  Vlad Gluhovsky for the basic specification of the Signidice algorithm and help in creation of this solution.
	\begin{thebibliography}{9}
\addcontentsline{toc}{section}{References}
\bibitem{bib11} Bitcoin Wiki: \url{https://en.bitcoin.it/wiki/Payment_channels}
\bibitem{bib10} Dan Boneh, Ben Lynn, and Hovav Shacham. \emph{Short signatures from the Weil pairing}. Computer Science Department, Stanford University \url{https://www.iacr.org/archive/asiacrypt2001/22480516.pdf}
\bibitem{bib16} Tom Close and Andrew Stewart. \emph{Force-Move Games}. June 21, 2018.
\bibitem{bib5} Jeff Coleman. \emph{State Channels.} \url{https://www.jeffcoleman.ca/state-channels/}. Nov 6, 2015
\bibitem{bib1} Jeff Coleman, Liam Horne, and Li Xuanji. \emph{Counterfactual: Generalized State Channels}. \url{https://l4.ventures/papers/statechannels.pdf}. June 12, 2018.
\bibitem{bib14} Stefan Dziembowski, Lisa Eckey, Sebastian Faust, Daniel Malinowski. \emph{PERUN: Virtual Payment Hubs over Cryptographic Currencies}.
\bibitem{bib20} Don Johnson, Alfred Menezes, Scott Vanstone. \emph{The Elliptic Curve Digital Signature Algorithm ECDSA}. February 24, 2000.
\bibitem{bib8} Amit Kumar Jaiswal. \emph{Parsec: A State Channel for the Internet of Value.} \url{https://arxiv.org/pdf/1807.11378.pdf}
\bibitem{bib26} Daniel Kraft. \emph{Game Channels for Trustless Off-Chain Interactions in Decentralized Virtual Worlds}. 2016.
\bibitem{bib15} Jeremy Longley and Oliver Hopton. \emph{Funfair technology roadmap and discussion}. \url{https://funfair.io/wp-content/uploads/FunFair-Technical-White-Paper.pdf}. 2017
\bibitem{bib17} Alex Lunyov, Johann Barbie, Konstantin Korenkov, Mayank Kumar. \emph{Multiparty State Channels Enabling Real-Time Poker on Ethereum}. \url{https://www.acebusters.com/files/acebusters_yellowpaper.pdf}
\bibitem{bib2} Ian Macalinao. \emph{Why EOS will overtake Ethereum in high performance smart contracts}. \url{https://ian.pw/posts/2017-12-08-why-eos-will-overtake-ethereum-in-high-performance-smart-contracts.html}
\bibitem{bib9} Patrick McCorry, Surya Bakshi, Iddo Bentov, Sarah Meiklejohn, Andrew Miller. \emph{Pisa: Arbitration Outsourcing for State Channels.} IC3, University College London, University of Illinois at Urbana Champaign, Cornell University. \url{https://www.cs.cornell.edu/~iddo/pisa.pdf}
\bibitem{bib7} Andrew Miller, Iddo Bentov, Ranjit Kumaresan, Patrick McCorry. \emph{Sprites: Payment Channels that Go Faster than Lightning}. UIUC, Cornell University, Microsoft Research, Newcastle University. \url{https://allquantor.at/blockchainbib/pdf/miller2017sprites.pdf}
\bibitem{bib24} Joseph Poon and Thaddeus Dryja. \emph{The bitcoin lightning network: Scalable off-chain instant payments}. \url{https://lightning.network/lightning-network-paper.pdf}. 2016.
\bibitem{bib25} Raiden specification. \url{http://raiden-network.readthedocs.io/en/stable/spec.html}. 2018.
\bibitem{bib19} R.L. Rivest, A. Shamir, and L. Adleman. \emph{A Method for Obtaining Digital Signatures and Public-Key Cryptosystems}. 1978.
\bibitem{bib3} Mark Schwarz. \emph{Transaction Speeds: Which Crypto Is the Fastest?} \url{https://www.abitgreedy.com/transactionspeed/transaction-speed}. June 26, 2018.
\bibitem{bib18} \emph{The Signidice Algorithm.} \url{https://github.com/gluk256/misc/blob/master/rng4ethereum/signidice.md}
\bibitem{bib4} Josh Stark. \emph{Making Sense of Ethereum’s Layer 2 Scaling Solutions: State Channels, Plasma, and Truebit.} \url{https://medium.com/l4-media/making-sense-of-ethereumslayer-2-scaling-solutions-state-channels-plasma-and-truebit-22cb40dcc2f4}
\bibitem{bib6} \emph{State Channels.} \url{https://github.com/aeternity/protocol/blob/master/channels/README.md}
\bibitem{bib23} C. Stathakopoulou, C. Cachin. \emph{Threshold Signatures for Blockchain Systems}. April 4, 2017. 
\bibitem{bib21} Team Keccak. \url{https://keccak.team/keccak.html}.
\bibitem{bib27} Xaya Game Library and Mover. \url{https://github.com/xaya/libxayagame}.
\end{thebibliography}


		

\end{document}